Reviewer comments from PeerJ

### 2015-02-19 PeerJResponse.tex
Edits to comments, additional files
Track changes document that is required for resubmission; Response
letter, edits to comments, list of things to address

\documentclass[11pt]{article}
\usepackage[letterpaper, margin=1in]{geometry} %package that allows changes in margins and header/footers
\newcommand{\jri}[1]{\noindent \textcolor{red}{{#1}} \\}
\newcommand{\lev}[1]{\noindent \textcolor{magenta}{{#1}} \\}
\newcommand{\mbh}[1]{\noindent \textcolor{Dandelion}{{#1}}\\}
\usepackage{lipsum}
\usepackage{url}
\usepackage[usenames,dvipsnames]{color}
\usepackage{multirow}
\renewcommand{\baselinestretch}{1.5}

@@

\title{Reviewer comments from PeerJ}
\textbf{Reviewer 1 (Anonymous)}\\

@@

3) Fig. 1 should indicate the boundaries of the Mexican states that are used in describing population locations in the text (Jalisco, Colima, etc.). The four focal populations from Jalisco state should also be labeled in this figure (i.e., San Lorenzo, La Mesa, Ejutla A, Ejutla B).\\
\lev{I think this would make figure super busy and it's already verging on super busy. Maybe compromise on labelling the four pops within their pie charts.} 
\mbh{if you still have access to the figure in ArcGIS, should be easy to add state boundaries and you can make the boundaries very light to limit busyness; if not, I'd just label the Jalisco pies}
\jri{raster in R is not too hard either.}

@@

5) Fig. S2. Annotate this figure to show the size (bp) of each band in the 1 kb ladder. The caption should also define the abbreviations used in the labels. \\
\lev{this will be too much. I can label the brightest band (1kb) and the top and bottom bands}
\mbh{I'd label as many as it takes so that it's obvious what intervening band sizes are.  We'll want to define the abbreviations too}

@@

\lev{Maybe in the text I can clarify total bands for individuals. I.e. if an individual is Hop/Hop, it will have a total of two bands that are split between the two PCRs, whereas if you are a heterozygote you will have 3 split between two PCRs. I wonder if we should ditch this figure entirely and I can draw up a cartoon one?}
\mbh{since reviewer 2 is also concerned about the PCR and this is the only thing the editor really mentioned, I think we need to be pretty thorough here.  Ideally we would have a Hop/Hop homozygote, a Hop/No Hop heterozygote, and a No Hop/No Hop homozygote in the figure.  We don't need the Pif since this really isn't mentioned in the manuscript.  Do you have gel figures showing both homozygotes and the heterozygote banding patterns? I'm afraid a cartoon would send the message that we don't have clear PCR results}
\jri{agree with the huff}

@@

8) Line 150. Why were only 100 bootstrap replicates used for the NJ analysis? 1000 is more typical.\\
\lev{I do not know the answer to this. I don't think that 1000 bootstraps would give us really a difference.}
\mbh{if you still have the input file for this analysis, should be a quick fix and show we're doing everything we can to address reviewer concerns}
\jri{agreed, should be easy to redo. while agree this is silly and i don't think 1000 will change anything, but since it's easy to do it's hard to argue against doing it.}

@@

@@

\mbh{my vote would be to remove the comparisons between \emph{parv} and \emph{mex} but to still note the high frequency in Jalisco}
\jri{ok either way here}

@@

\mbh{Jeff and I will address this}
\jri{sloppy my ass. <censored> reviewer!}

\textbf{Reviewer 2 (Anonymous)}

@@

2) The authors refer several times to a previous study they performed: Pyhäjärvi et al., 2013. This is fine, but it is not always easy to understand which results are new and which come from this previous study. For instance, on line 158, it is stated 'we had whole genome SNP data come from Pyhäjärvi et al., 2013. Similarly, Table 1 on line 217 should be moved right after 'populations (0.23) on line 216 to avoid confusion.\\

@@

\lev{Okay. Is there somewhere we can get all of this info.? I don't believe I have access to the database any more}
\mbh{Yes, we need to include this info.; that's a fair request}

@@

\mbh{we need to check this.  can you go back through emails or to your lab notebook to find whether this was sequenced?}
\jri{i don't remember ever checking this. we checked the pif by PCRing stuff John had already sequenced in which i identified the pif}

@@

>>>>

\documentclass[11pt]{article}
\usepackage[letterpaper, margin=1in]{geometry} %package that allows changes in margins and header/footers
\newcommand{\res}[1]{\noindent \textcolor{blue}{{#1}} \\}
\newcommand{\jri}[1]{\noindent \textcolor{red}{{#1}} \\}
\newcommand{\lev}[1]{\noindent \textcolor{green}{{#1}} \\}
\newcommand{\mbh}[1]{\noindent \textcolor{Dandelion}{{#1}}\\}
\usepackage{lipsum}
\usepackage{url}
\usepackage[usenames,dvipsnames]{color}
\usepackage{multirow}
\renewcommand{\baselinestretch}{1.5}
\usepackage{natbib} % package for formatting citations
%\bibliographystyle{AJB} %indicating bibliography uses the AJB.bst file for

@@

\noindent Dear Dr.Vision and editorial staff at the \emph{PeerJ}, \\

We would like to thank you and two anonymous reviewers for your helpful comments and suggestions regarding our previously-submitted manuscript (#2014:12:3442:0:0:REVIEW).  In the attached revision, we have addressed the majority of issues raised, and have included a detailed response to reviewers below.  In our submitted manuscript, we report results of a genotyping assay surveying several hundred wild and domesticated maize individuals for presence of the domesticated maize allele at \emph{tb1}, Sanger sequencing of a targeted subset of these samples to assess evidence of selection on the domesticated allele in wild populations, a phenotyping experiment to gauge the effects of the domesticated allele in a wild population, and reanalysis of existing genome-wide SNP data to place the signature of selection at this locus in a wider context.  This manuscript reports a substantial amount of novel work and explores, in a meaningful way, the concept of domestication from standing variation and the potential ecological relevance of domesticated alleles in wild populations.\\\

\noindent Sincerely,\\

\noindent Matthew Hufford and Jeffrey Ross-Ibarra

\section*{Response to Editor:}

1) The reviewers comments seems to be largely in agreement and self-explanatory. Please be sure to address the comment regarding the validity of the PCR assays raised by Reviewer 2.

\res{We have addressed the comments from Reviewer 2 regarding the validity of the PCR assays. Sequencing of PCR products was never performed as primer combinations for each of the 2 PCRs gave us the expected sized bands. Primers were designed off of previously sequenced teosinte and maize sequences \lev{these were from John Doebley, do we need to say this? I don' think they were published ever} and were initially tested in both maize and teosinte for validity.  We have clarified this point in text \lev{text, line numbers here} as well added additional labelling to the gel image (Figure 2 \lev{check to make sure figure number doesn't change during edits}).

\section*{Response to Reviewer 1}

@@

3) Fig. 1 should indicate the boundaries of the Mexican states that are used in describing population locations in the text (Jalisco, Colima, etc.). The four focal populations from Jalisco state should also be labeled in this figure (i.e., San Lorenzo, La Mesa, Ejutla A, Ejutla B).\\
\lev{I think this would make figure super busy and it's already verging on super busy. Maybe compromise on labelling the four pops within their pie charts.} 
\mbh{if you still have access to the figure in ArcGIS, should be easy to add state boundaries and you can make the boundaries very light to limit busyness; if not, I'd just label the Jalisco pies}
\jri{raster in R is not too hard either.}
\lev{I do not have access to the either the figure in ArcGIS or ArcGIS, so will just label the pies in something else and call it a day}

@@

5) Fig. S2. Annotate this figure to show the size (bp) of each band in the 1 kb ladder. The caption should also define the abbreviations used in the labels. \\
\lev{this will be too much. I can label the brightest band (1kb) and the top and bottom bands}
\mbh{I'd label as many as it takes so that it's obvious what intervening band sizes are.  We'll want to define the abbreviations too}
\lev{usually the bottom, middle brightest and top are labelled so I will do that}

@@

\lev{Maybe in the text I can clarify total bands for individuals. I.e. if an individual is Hop/Hop, it will have a total of two bands that are split between the two PCRs, whereas if you are a heterozygote you will have 3 split between two PCRs. I wonder if we should ditch this figure entirely and I can draw up a cartoon one?}
\mbh{since reviewer 2 is also concerned about the PCR and this is the only thing the editor really mentioned, I think we need to be pretty thorough here.  Ideally we would have a Hop/Hop homozygote, a Hop/No Hop heterozygote, and a No Hop/No Hop homozygote in the figure.  We don't need the Pif since this really isn't mentioned in the manuscript.  Do you have gel figures showing both homozygotes and the heterozygote banding patterns? I'm afraid a cartoon would send the message that we don't have clear PCR results}
\jri{agree with the huff}
\lev{I do not have gel figures. I am guessing the ones that had been saved online in Jeff's lab have been tossed. I can check my lab notebook and see if there is something to scan, otherwise there will not be a figure with all of those genotypes that we can give to them.}

@@

8) Line 150. Why were only 100 bootstrap replicates used for the NJ analysis? 1000 is more typical.\\
\lev{I do not know the answer to this. I don't think that 1000 bootstraps would give us really a difference.}
\mbh{if you still have the input file for this analysis, should be a quick fix and show we're doing everything we can to address reviewer concerns}
\jri{agreed, should be easy to redo. while agree this is silly and i don't think 1000 will change anything, but since it's easy to do it's hard to argue against doing it.}
\lev{I do not have the files as this is something that Tom did with the sequence data that he gathered}

@@

\lev{I believe that she phased it since it was the exact thing that she used for her BayEnv stuff}

@@

\mbh{my vote would be to remove the comparisons between \emph{parv} and \emph{mex} but to still note the high frequency in Jalisco}
\jri{ok either way here}
\lev{I vote remove since everyone has seemed unhappy with this}

@@

\mbh{Jeff and I will address this}
\jri{sloppy my ass. <censored> reviewer!}
\lev{ :) }

\section*{Response to Reviewer 2}

@@

2) The authors refer several times to a previous study they performed: Pyh√§j√§rvi et al., 2013. This is fine, but it is not always easy to understand which results are new and which come from this previous study. For instance, on line 158, it is stated 'we had whole genome SNP data come from Pyh√§j√§rvi et al., 2013. Similarly, Table 1 on line 217 should be moved right after 'populations (0.23) on line 216 to avoid confusion.\\

@@

\lev{Okay. Is there somewhere we can get all of this info.? I don't believe I have access to the database any more}
\mbh{Yes, we need to include this info.; that's a fair request}
\lev{Do either of you know where I can find this info?}

@@

\mbh{we need to check this.  can you go back through emails or to your lab notebook to find whether this was sequenced?}
\jri{i don't remember ever checking this. we checked the pif by PCRing stuff John had already sequenced in which i identified the pif}
\lev{I agree with Jeff. I believe bands matched with what was expected based on where we designed primers so we did not sequence them}

@@

\bibliography{refs}
